---
title: "Milestone Eight"
author: "Sam Lowry"
date: "4/27/2020"
output: bookdown::pdf_document2
bibliography: bib.bib
biblio-style: "apalike"
fontsize: 12pt
linestretch: 1.5
abstract: Campbell et al. (2019) which details two separate experiments which suggest that individuals think of politicians with local roots and that exibit behavioral localism more highly. I was able to replicate the entire article with the exceptions of table 1 and figure 2 because they visuals relating to methodology and not the results themselves. I will be conducting an extension which includes the use of stan_glm instead of lm as well as look at certain subgroups based upon location and party identification. I hope to find cool things:)
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(bookdown)
library(sandwich)
library(lmtest)
library(stargazer)
library(cowplot)
library(cobalt)
library(xtable)
library(devtools)
library(margins)
library(car)
library(foreign)
library(rms)
library(reshape2)
library(plyr)
library(arm)
library(huxtable)
library(factorEx)
library(dotwhisker)
library(rstanarm)
library(tidyverse)
```

```{r options}
options(huxtable.print = "latex")
```

# Introduction

@paper aims to answer the driving question of, "Why do politicians with strong local roots receive more electoral support?" by running and analyzing two separate studies. The first study uses a "paired profiles factorial vignette design" by asking subjects to rate hypothetical members of Parliament. The hypothetical members have varying levels of local roots as well as varying levels of "behavioral localism"—their track record of constituency service and if they act more so as a trustee or delegate. In the second study, subjects again considered hypothetical members of Parliament with varying levels of local roots. How, the subjects also received information on their political preferences and partisan loyalties. The first study depicted that the additional information swayed rankings, but local roots still seemed to have an association. The second study agreed with these results stating that, "even if voters are provided with a rich array of information about politicians’ behavior and ideological positioning, the effect of local roots remained positive and notable." The remainder of the article discusses the nuances of these results within the frame of the driving question.

Using R, I replicated @paper. The original code can be found in the \textit{The Journal of Politics} Dataverse.^[https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/C15VOD] All of my code for this paper including the extension is available in my Github repository.^[https://github.com/SamuelLowry/why_friends_and_neighbors_replication_paper.git]

# Literature Review

Due to @paper being a very recent article, published May 6, 2019, there has not been any follow-up scholarly work on the topic even from the authors themselves. Nevertheless, @paper builds off of a rich history of the "friends and neighbors" effect which was first coined by @key. Other noteable works include @bowler and @garand which highlight the United States and @arzheimer as well as @arzheimer2 which highlight Britain. These two articles are particularly important due to @paper dealing with the "friends and neighbors" effect in the United Kingdom. These are just a couple of the noteable works. Of course, more in way of an actual review is to come.

# Paper Review 

@paper aims to answer the driving question of, "Why do politicians with strong local roots receive more electoral support?" by running and analyzing two separate studies. The first study uses a "paired profiles factorial vignette design" by asking subjects to rate hypothetical members of Parliament. The hypothetical members have varying levels of local roots as well as varying levels of "behavioral localism"—their track record of constituency service and if they act more so as a trustee or delegate. In the second study, subjects again considered hypothetical members of Parliament with varying levels of local roots. How, the subjects also received information on their political preferences and partisan loyalties. The first study depicted that the additional information swayed rankings, but local roots still seemed to have an association. The second study agreed with these results stating that, "even if voters are provided with a rich array of information about politicians’ behavior and ideological positioning, the effect of local roots remained positive and notable." The remainder of the article discusses the nuances of these results within the frame of the driving question.

# Replication 

Using R, I was able to replicate all of @paper. All of the code needed to do the same can be found within the Appendix. 

# Extension

I have already been able to replicate all of the results from \textit{Why Friends and Neighbors? Explaining the Electoral Appeal of Local Roots} @paper by Rosie Campbell, Philip Cowley, Nick Vivyan, and Markus Wagner in the \textit{The Journal of Politics}. The next step is to improve upon their methods and make suggests as to what to do next. My thoughts are below:

1. Use stan_glm instead of lm for study 1
2. Look at heterogeneous effects for study 1
3. Look at population effects for study 2
4. Use a pAMCE for study 2 instead of an AMCE

\newpage

## Study 1

```{r extensiondata}
#loaded in the data from the first study

d <- readRDS("paper_files/study1data.rds")

long.dat <- readRDS("paper_files/study2data_long.rds")
```

<left>

```{r stan, fig.cap= "Bayesian Generalized Linear Models", warning=FALSE, message=FALSE, fig.align= "l"}
stan_m1 <- stan_glm(nickminusphil ~ localtreat*behtreatsimple, data = d, refresh = FALSE)

stan_m2 <- stan_glm(nickminusphil ~ localtreat*behtreatsimple + gender + agegrp + socgrade + qual,
                    data = d, 
                    refresh = FALSE)

stan_m3 <- stan_glm(nickminusphil ~ localtreat*behtreat, data = d, refresh = FALSE)

stan_m4 <- stan_glm(nickminusphil ~ localtreat*behtreat + gender + agegrp + socgrade + qual,
                    data = d, 
                    refresh = FALSE)

hux_1 <- huxreg(stan_m1, stan_m2, stan_m3, stan_m4,
                statistics = NULL,
                stars = NULL,
                error_pos = "same",
                coefs = c('Intercept' = '(Intercept)',
                          "Has Local Roots" = "localtreatLocal roots",
                          "Behavioral Info Given" = "behtreatsimpleBehavioural info",
                          "Treatments Interaction" = "localtreatLocal roots:behtreatsimpleBehavioural info",
                          "Male" = "genderMale",
                          "25-49" = "agegrp25-49",
                          "50-64" = "agegrp50-64",
                          "65+" = "agegrp65+",
                          "Skilled Working Class" = "socgradeC2",
                          "Lower Middle Class" = "socgradeC1",
                          "Middle Class" = "socgradeAB",
                          "GCSE" = "qualLevel 1/2",
                          "A Levels" = "qualLevel 3",
                          "University" = "qualLevel 4",
                          "Constituency Focus" = "behtreatConst. focus",
                          "National Focus" = "behtreatWestmin. focus",
                          "Local:Constituency" = "localtreatLocal roots:behtreatConst. focus",
                          "Local:National" = "localtreatLocal roots:behtreatWestmin. focus"))

hux_1 <- hux_1 %>%
  set_caption('Bayesian Generalized Linear Models Instead of Linear Models')

width(hux_1) <- 1

hux_1

```


</left>

Here, the four models are created using stan_glm instead of the traditional lm. The contents of the parentheses present the MAD SD and not a traditional standard error. 

\newpage

<left>

```{r soc}

d_d <- d %>% filter(socgrade == "DE")

d_c2 <- d %>% filter(socgrade == "C2")

d_c1 <- d %>% filter(socgrade == "C1")

d_a <- d %>% filter(socgrade == "AB")

stan_d <- stan_glm(nickminusphil ~ localtreat*behtreat,
                    data = d_d, 
                    refresh = FALSE)

stan_c2 <- stan_glm(nickminusphil ~ localtreat*behtreat,
                    data = d_c2, 
                    refresh = FALSE)

stan_c1 <- stan_glm(nickminusphil ~ localtreat*behtreat,
                    data = d_c1, 
                    refresh = FALSE)

stan_a <- stan_glm(nickminusphil ~ localtreat*behtreat,
                    data = d_a, 
                    refresh = FALSE)

dwplot(list(stan_a, stan_c1, stan_c2, stan_d),
       dodge_size = .6) %>% 
  relabel_predictors(c("(Intercept)" = "Intercept",                   
                     "localtreatLocal roots" = "Local Roots (Baseline = None) \nLocal Roots",          
                     "behtreatConst. focus" = "Behavioral Information (Baseline = None) \nConstituency Focus",
                     "behtreatWestmin. focus" = "National Focus",
                     "localtreatLocal roots:behtreatConst. focus" = "Interaction Terms \nLocal:Constituency Focus",
                     "localtreatLocal roots:behtreatWestmin. focus" = "Local:National Focus")) + 
  geom_vline(xintercept = 0, colour = "grey60", linetype = 2) +
  scale_colour_hue(name = "Social Class",
                     labels = c("Middle", "Lower Middle", "Skilled Working", "Unskilled Working")) +
  theme(legend.text = element_text(size = 6),
        legend.title = element_text(size = 8),
        legend.position = c(.163, .81)) +
  labs(title = "Treatment Coefficients Across Social Classes",
       x = "Coefficient Value")

```

</left>

\newpage

## Study 2


I also wanted to look at the urban/rural divide, so I compared London, the only completely urban region within the UK with the rest of the UK regions. These tables appear to be almost identical and can be compared to figure 3 of @paper. 

<left>

```{r conjoint}

long.dat_18 <- long.dat %>% filter(age_grouped == "18-24")

long.dat_25 <- long.dat %>% filter(age_grouped == "25-39")

long.dat_40 <- long.dat %>% filter(age_grouped == "40-59")

long.dat_60 <- long.dat %>% filter(age_grouped == "60+")

conjoint_18 <- lm(formula = mp.preferred ~ mp.partypos + mp.localroots + mp.const + mp.influence + mp.policy + mp.gender, data = long.dat_18)

conjoint_25 <- lm(formula = mp.preferred ~ mp.partypos + mp.localroots + mp.const + mp.influence + mp.policy + mp.gender, data = long.dat_25)

conjoint_40 <- lm(formula = mp.preferred ~ mp.partypos + mp.localroots + mp.const + mp.influence + mp.policy + mp.gender, data = long.dat_40)

conjoint_60 <- lm(formula = mp.preferred ~ mp.partypos + mp.localroots + mp.const + mp.influence + mp.policy + mp.gender, data = long.dat_60)


dwplot(list(conjoint_18, conjoint_25, conjoint_40, conjoint_60),
       dodge_size = .6) %>% 
  relabel_predictors(c("(Intercept)" = "Intercept",                   
                     "mp.partyposLabour centre" = "Party (Baseline = Labour Left-wing) \nLabour Centre",          
                     "mp.partyposConservative centre" = "Conservative Centre",
                     "mp.partyposConservative right-wing" = "Conservative Right-wing",
                     "mp.localroots5 years in area" = "Local Roots (Baseline = Lives Elsewhere) \n5 Years in Area",
                     "mp.localroots20 years in area" = "20 years in area",
                     "mp.localrootsGrew up and lives in area" = "Grew up and Lives in Area",
                     "mp.const2 days" = "Constituency Work (Baseline = 1 Day) \n 2 days",
                     "mp.const3 days" = "3 Days",
                     "mp.const4 days" = "4 Days",
                     "mp.influenceConstituents" = "Policy Influence (Baseline = Party) \nConstituents' Views",
                     "mp.influenceOwn personal" = "Own Personal Views",
                     "mp.policyEducation and health" = "Policy Focus (Baseline = Economy and Tax) \nEducation and Health",
                     "mp.genderMale" = "Sex (Baseline = Female) \nMale")) + 
  geom_vline(xintercept = 0, colour = "grey60", linetype = 2) +
  scale_colour_hue(name = "Age Group",
                     labels = c("18-24", "25-39", "40-59", "60+")) +
  theme(legend.position = c(.155, .5)) +
  labs(title = "Average Marginal Component Effects \nby Age Group",
       x = "Change in Probability of MP Being Preferred")

```

</left>








<left>

```{r conjoint interaction, fig.height = 6}

conjoint <- lm(formula = mp.preferred ~ mp.partypos + mp.localroots + mp.const + mp.influence + mp.policy + mp.gender, data = long.dat)


#This is interesting because is shows that we see less care about policy influence with increase in local roots

conjoint_interaction <- lm(formula = mp.preferred ~ mp.partypos + mp.localroots + mp.const + mp.influence + mp.policy + mp.gender + mp.localroots:mp.influence,
                           data = long.dat)

#grew up significant at 95% confidence for both

dwplot(list(conjoint, conjoint_interaction)) %>% 
   relabel_predictors(c("(Intercept)" = "Intercept",                   
                     "mp.partyposLabour centre" = "Party (Baseline = Labour Left-wing) \nLabour Centre",          
                     "mp.partyposConservative centre" = "Conservative Centre",
                     "mp.partyposConservative right-wing" = "Conservative Right-wing",
                     "mp.localroots5 years in area" = "Local Roots (Baseline = Lives Elsewhere) \n5 Years in Area",
                     "mp.localroots20 years in area" = "20 years in area",
                     "mp.localrootsGrew up and lives in area" = "Grew up and Lives in Area",
                     "mp.const2 days" = "Constituency Work (Baseline = 1 Day) \n 2 days",
                     "mp.const3 days" = "3 Days",
                     "mp.const4 days" = "4 Days",
                     "mp.influenceConstituents" = "Policy Influence (Baseline = Party) \nConstituents' Views",
                     "mp.influenceOwn personal" = "Own Personal Views",
                     "mp.policyEducation and health" = "Policy Focus (Baseline = Economy and Tax) \nEducation and Health",
                     "mp.genderMale" = "Sex (Baseline = Female) \nMale",
                     "mp.localroots5 years in area:mp.influenceConstituents" = "Interaction Terms \n5 Years:Constituents' Views",
                     "mp.localroots20 years in area:mp.influenceConstituents" = "20 Years:Constituents' Views",
                     "mp.localrootsGrew up and lives in area:mp.influenceConstituents" = "Grew up:Constituents' Views",
                     "mp.localroots5 years in area:mp.influenceOwn personal" = "5 Years:Own Personal",
                     "mp.localroots20 years in area:mp.influenceOwn personal" = "20 Years:Own Personal",
                     "mp.localrootsGrew up and lives in area:mp.influenceOwn personal" = "Grew up:Own Personal")) +
  geom_vline(xintercept = 0, colour = "grey60", linetype = 2) +
  scale_colour_hue(name = "AMCE Type",
                     labels = c("Without \nInteraction Terms", "With \nInteraction Terms")) +
  theme(legend.text = element_text(size = 8),
        legend.title = element_text(size = 10),
        legend.position = c(.18, .7)) +
  labs(title = "Average Marginal Component Effects with Interaction",
       x = "Change in Probability of MP Being Preferred")
```

</left>

This has yet to be completed, but study 2 utilizes AMCE in their analysis of the conjoints. Nevertheless, as pointed out in @pamce, "MCE critically relies upon the distribution of the other attributes used for the averaging. Although most employ uniform distribution, which equally weights each profile, both the actual distribution of profiles in the real world and the distribution of theoretical interest are often far from uniform." Therefore they propose the use of pAMCE using the factorEx R package which takes population into account. I aim to utilize this instead of AMCE as a further extension. 

These extensions hopefully better the article as a whole and clarify its implications. 

\newpage

# Conclusion

There is little difference between the stan_glm and the lm. I have yet to figure out the pAMCE. More is to come!

\newpage

# References

<div id="refs"></div>

\newpage

# (APPENDIX) Appendix {-} 

# Appendix of Replicated Graphics

I was able to replicate table 2, figure 1, and figure 3. They are below. I was unable to replicate table 1 and figure 2 because they were not data related. They were merely visualizations displaying content about methods and experimental design. Table 1 depicts written descriptions of the hypothetical Members of Parliament present to subject. Figure 2 depicts a screenshot of the survey. 

### Table 2 {-} 

```{r data}
#loaded in the data from the first study

d <- readRDS("paper_files/study1data.rds")

```

```{r table2, warning=FALSE, results='asis'}
#warning = FALSE in order to get rid of unknown variable due to their code being wacl

#Here I pulled over their code but then tried to improve upon it, for currently the figure is unreadable. 

#models for this graphic and the table later on

m1 <- lm(nickminusphil ~ localtreat*behtreatsimple, data = d)
se1 <- sqrt(diag(vcovHC(m1)))

m2 <- lm(nickminusphil ~ localtreat*behtreatsimple +
           gender + agegrp + socgrade + qual
         , data = d)
se2 <- sqrt(diag(vcovHC(m2)))

m3 <- lm(nickminusphil ~ localtreat*behtreat, data = d)
se3 <- sqrt(diag(vcovHC(m3)))

m4 <- lm(nickminusphil ~ localtreat*behtreat +
           gender + agegrp + socgrade + qual
         , data = d)
se4 <- sqrt(diag(vcovHC(m4)))

#I took the code for table 2 from their code and made it output to Latex

stargazer(mget(paste0("m",1:4)),
          se = mget(paste0("se",1:4)),
          type = "latex",
          float = FALSE,
          dep.var.caption = "",
          dep.var.labels.include = FALSE,
          title = "",
          header = FALSE,
          #intercept.bottom = FALSE, intercept.top = TRUE,
          keep.stat = c("n", "rsq", "adj.rsq"),
          omit = "socgrade|agegrp|gender|qual",
          order = c("Constant", "^localtreatLocal roots$", 
                    "^behtreatsimpleBehavioural info$", 
                    "^behtreatConst. focus$", 
                    "^behtreatWestmin. focus$",
                    "^localtreatLocal roots:behtreatsimpleBehavioural info$",
                    "^localtreatLocal roots:behtreatConst. focus$",
                    "^localtreatLocal roots:behtreatWestmin. focus$"
          ),
          add.lines = list(c("Controls for voter characteristics?", 
                             rep(c("No","Yes"), 2))),
          covariate.labels = c("Intercept", "Local roots", "Behavioral localism information",
                               "Behavioral localism: High (vs. no info)",
                               "Behavioral localism: Low (vs. no info)",
                               "Local roots X Behavioral info.", 
                               "Local roots X High behavioral localism",
                               "Local roots X Low behavioral localism")
)
```

Note from @paper: "All models estimated via ordinary least squares. Dependent variable is respondent relative rating of MP Nick (the 0–10 rating of Nick minus that of Philip). Robust standard errors in parentheses. N p 5,203."

### Figure 1 {-}

```{r figure1, warning = FALSE, cache = TRUE}

#warning is false to delete warning for unknown variable specified in code which does not change vizualization from the paper. 

#function needed for figure 1

predict.rob <- function(object, vcov,newdata){
  tt <- terms(object)
  if(missing(newdata)){ newdata <- x$model }
  else {
    Terms <- delete.response(tt)
    m <- model.frame(Terms, newdata, na.action = na.pass, 
                     xlev = object$xlevels)
    if (!is.null(cl <- attr(Terms, "dataClasses"))) 
      .checkMFClasses(cl, m)
    X <- model.matrix(Terms, m, contrasts.arg = object$contrasts)
    offset <- rep(0, nrow(X))
    if (!is.null(off.num <- attr(tt, "offset"))) 
      for (i in off.num) offset <- offset + eval(attr(tt, 
                                                      "variables")[[i + 1]], newdata)
    if (!is.null(object$call$offset)) 
      offset <- offset + eval(object$call$offset, newdata)
    mmDone <- FALSE
  }
  #m.mat <- model.matrix(x$terms,data=newdata)
  m.coef <- object$coef
  fit <- as.vector(X %*% object$coef)
  se.fit <- sqrt(diag(X%*%vcov%*%t(X)))
  return(list(fit=fit,se.fit=se.fit))
}


### Figure 1
#I was very confused about B here especially because of the variability and the "no information" section being higher. 
## Avg treatment effect of local roots with const and westmihn. info
out <- summary(margins(m4, vcov = vcovHC(m4), 
                       at = list(behtreat = c("No behavioural info", "Const. focus", "Westmin. focus"))))
out <- subset(out, factor == "localtreatLocal roots")
margins.m4 <- out 

## make margins plot
margins.comb <- margins.m4
margins.comb$behtreat.neat <- car:::recode(margins.comb$behtreat, 
                                           '"No behavioural info" = "Behavioral information treatment --\\nNo information (Vignettes 1-2)";
                                           "Westmin. focus" = "Behavioral information treatment --\\nLow behavioral localism (Vignettes 5-6)";
                                           "Const. focus" = "Behavioral information treatment --\\nHigh behavioral localism (Vignettes 3-4)"')
margins.comb$behtreat.neat <- factor(sub(" --", ":", margins.comb$behtreat.neat),
                                     levels = c("Behavioral information treatment:\nNo information (Vignettes 1-2)", 
                                                "Behavioral information treatment:\nLow behavioral localism (Vignettes 5-6)",
                                                "Behavioral information treatment:\nHigh behavioral localism (Vignettes 3-4)"
                                     ))
p1 <- ggplot(margins.comb, aes(x = factor, y = AME)) + 
  geom_hline(yintercept = 0, linetype = "dashed", size = 0.5) +
  geom_linerange(aes(x=factor, xend=factor, ymin=lower, ymax=upper), size = 0.6) +
  geom_point(size = 3.5, shape = 21, fill = "white") +
  labs(x = "", y = "") + 
  coord_flip() +
  facet_wrap( ~ behtreat.neat, ncol = 1) + 
  theme_bw() +
  theme(legend.position = "bottom") +
  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()) + 
  ggtitle("(b) Effect of MP local\ntreatment") 




## predlevels for m4
#what is m4???
newdf <- data.frame(expand.grid(localtreat = factor(c("No local roots", "Local roots"), 
                                                    levels = levels(d$localtreat)),
                                behtreat = factor(levels(d$behtreat), levels = levels(d$behtreat))
),
gender = factor(levels(d$gender)[which.max(table(d$gender))], 
                levels = levels(d$gender)),
agegrp = factor(levels(d$agegrp)[which.max(table(d$agegrp))], 
                levels = levels(d$agegrp)),
socgrade = factor(levels(d$socgrade)[which.max(table(d$socgrade))], 
                  levels = levels(d$socgrade)),
qual = factor(levels(d$qual)[which.max(table(d$qual))], 
              levels = levels(d$qual))
)
preds <- predict.rob(m4, vcov = vcovHC(m4), newdata = newdf)
newdf$yhat <- preds$fit
newdf$se.yhat <- preds$se.fit
newdf$lo <- newdf$yhat - (1.96*newdf$se.yhat)
newdf$hi <- newdf$yhat + (1.96*newdf$se.yhat)
predlevels.m4 <- newdf


## make predlevels plot
#okay this is still the first plot. B still confuses me though. 
predlevels.comb <- predlevels.m4
predlevels.comb$behtreat.neat <- car:::recode(predlevels.comb$behtreat, 
                                              '"No behavioural info" = "Behavioral information treatment --\\nNo information (Vignettes 1-2)";
                                              "Westmin. focus" = "Behavioral information treatment --\\nLow behavioral localism (Vignettes 5-6)";
                                              "Const. focus" = "Behavioral information treatment --\\nHigh behavioral localism (Vignettes 3-4)"')
predlevels.comb$behtreat.neat <- factor(sub(" --", ":", predlevels.comb$behtreat.neat),
                                        levels = c("Behavioral information treatment:\nNo information (Vignettes 1-2)", 
                                                   "Behavioral information treatment:\nLow behavioral localism (Vignettes 5-6)",
                                                   "Behavioral information treatment:\nHigh behavioral localism (Vignettes 3-4)"
                                        ))

p2 <- ggplot(predlevels.comb, aes(x = localtreat, y = yhat)) + 
  geom_hline(yintercept = 0, linetype = "dashed", size = 0.5) +
  geom_linerange(aes(x=localtreat, xend=localtreat, ymin=lo, ymax=hi), size = 0.6) +
  geom_point(size = 3.5, shape = 21, fill = "white") +
  labs(x = "", y = "") + 
  coord_flip() +
  facet_wrap( ~ behtreat.neat, ncol = 1) + 
  theme_bw() +
  theme(legend.position = "bottom") + 
  ggtitle("(a) Predicted relative rating")



## Now combine aspects of above plots into 3 x 2 plot
pcomb <- plot_grid(p2, p1, align = "h", rel_widths = c(1,0.8))

pcomb
```

Caption from @paper: "Figure 1. Effects of local roots conditional on behavioral information treatments (study 1). A, Predicted relative rating of MP Nick (MP Nick rating minus MP Philip rating) as the MP local roots treatment varies, with all control variables held constant at their modal value in the sample. Top, predicted values when respondents receive no information about MP behavioral localism. Middle, predicted values when respondents receive information about MP behavioral localism and Nick is revealed to be low in behavioral localism. Bottom, predicted values when respondents receive information about MP behavioral localism and Nick is revealed to be high in behavioral localism. For each of the same behavioral localism conditions, B show the estimated treatment effect of MP Nick having local roots. Estimates are calculated from model 4 in table 2. Open circles indicate point estimates. Lines denote 95% confidence intervals."

### Figure 3 {-}

```{r figure3, warning = FALSE, fig.cap="Figure 3. Estimated average marginal component effects of each MP attribute level compared to the baseline level of the attribute, estimated via ordinary least squares regression, with standard errors clustered by respondent. Bars show 95% confidence intervals"}

#warning is false to delete warning for 11 deletions caused by ggplot which does not change vizualization from the paper. 

#needed data

long.dat <- readRDS(file = "paper_files/study2data_long.rds")

### Create labels for plotting

# for full results
labels.full <- rev(expression(
  "", italic("Party & position (baseline = Labour left-wing)"), "Labour centre", "Conservative centre", "Conservative right-wing",
  "", italic("Local roots (baseline = lives elsewhere)"),"5 years in area", "20 years in area", "Grew up and lives in area", 
  "", italic("Constituency work (baseline = 1 day)"), "2 days", "3 days", "4 days",
  "", italic("Main policy influence (baseline = party)"), "constituents' views","own personal views",
  "", italic("Policy interests (baseline = economy and tax)"), "education and health",
  "", italic("MP sex (baseline = female)"), "male"))

# for x axis
effect.label <- "Change in probability of MP being\npreferred relative to baseline"

#needed functions

add.top <- function(df, new.level){
  to.add <- data.frame(mean = c(NA,NA, 0), ci.lo = c(NA,NA, 0), ci.hi = c(NA,NA, 0),
                       category = rep("", 3), attribute = rep(df$attribute[1],3),
                       level = c("", " ", new.level))
  return(rbind(to.add, df))
}
add.justify <- function(df){
  df$left.justify <- rep(0, nrow(df))
  df$left.justify[2] <- 1
  return(df)
}

## Function to get regression-based AMCE estimates for each attribute level using 
## OLS estimator with clustered SEs (Hainmueller, Hopkins and Yammamoto 2014)

#Note to read up on the other literature above

get.amcetab <- function(data, variables, J = 2){    
  Nvar <- length(variables)
  amce.list <- vector("list", length = Nvar)
  
  for(i in 1:Nvar){ # get AMCE for each variable attribute
    fmla <- as.formula(paste("mp.preferred ~ ",variables[i], sep = ""))
    model <- ols(fmla, data = data, x = T, y = T) 
    # NOTE: The data for the model has to have no NAs on any model variables 
    # for the robcov(cluster()) function to work 
    model.clus <- robcov(model, cluster = data$ID, method = "efron")
    coef <- model.clus$coef[names(model.clus$coef)!="Intercept"]
    se.clus <- sqrt(diag(model.clus$var))
    se.clus <- se.clus[names(se.clus)!="Intercept"]       
    sub.tab <- data.frame("AMCE" = coef, 
                          "ci.lo" = coef - (1.96*se.clus),
                          "ci.hi" = coef + (1.96*se.clus),
                          "cluster.se" = se.clus)
    sub.tab$category <- names(coef)
    sub.tab <- cbind(sub.tab, colsplit(sub.tab$category, "=", c("attribute","level")))
    sub.tab$level <- as.character(sub.tab$level)    
    row.names(sub.tab) <- NULL
    # add in gaps and baselines
    to.add <- data.frame(AMCE = c(NA,NA, 0), ci.lo = c(NA,NA, 0), ci.hi = c(NA,NA, 0),
                         cluster.se = c(NA,NA, 0),
                         category = rep("", 3), attribute = rep(sub.tab$attribute[1],3),
                         level = c("", " ", "baseline"))
    amce.list [[i]] <- rbind(to.add, sub.tab)
  } 
  amce.tab <- do.call("rbind", amce.list)
  # re-make initial labels column
  amce.tab$category <- paste(amce.tab$attribute, amce.tab$level, sep = ": ")
  # make this into ordered factor
  amce.tab$category <- factor(amce.tab$category, levels = rev(amce.tab$category), order =T)    
  
  return(amce.tab)
}

## Function that calls get.amcetab for multiple predictors and combines results

amce.tab <- function(data, variables, multi = F, same.party = F){
  # data must be a single data frame or a list of data frames (if multi = T)
  # with named elements
  # Also relies on specific ordering of explanatory variables
  if(multi == T & same.party == F){
    amce.tab.list <- list(NA, length = length(data))
    for(i in 1:length(data)){
      tmp <- get.amcetab(data[[i]], variables = variables)
      tmp$set <- rep(names(data)[i], nrow(tmp))
      amce.tab.list[[i]] <- tmp
    }
    amce.tab <- do.call("rbind",amce.tab.list)
    amce.tab$set <- factor(amce.tab$set)
    return(amce.tab)
  }
  if(multi == T & same.party == T){
    amce.tab.list <- list(NA, length = length(data))
    for(i in 1:length(data)){
      vars <- if(grepl("same party", names(data)[i])==T|grepl("Same Party", names(data)[i])==T) variables[2:length(variables)] else variables
      tmp <- get.amcetab(data[[i]], variables = vars)
      tmp$set <- rep(names(data)[i], nrow(tmp))
      amce.tab.list[[i]] <- tmp
    }
    names(amce.tab.list) <- names(data)
    diff.party <- amce.tab.list[grepl("same party", names(amce.tab.list))==F&
                                  grepl("Same Party", names(amce.tab.list))==F]
    same.party <- amce.tab.list[grepl("same party", names(amce.tab.list))==T |
                                  grepl("Same Party", names(amce.tab.list))==T]
    to.add <- data.frame(AMCE = rep(NA, 4), ci.lo = rep(NA, 4), ci.hi =  rep(NA, 4),
                         cluster.se =  rep(NA, 4),
                         category =  diff.party[[1]]$category[1:4], 
                         attribute =  diff.party[[1]]$attribute[1:4], 
                         level = diff.party[[1]]$level[1:4],
                         set = rep(NA, 4))
    for(i in 1:length(data)){                     
      if(grepl("same party", names(data)[i])==T|grepl("Same Party", names(data)[i])==T){
        amce.tab.list[[i]] <- rbind(to.add,amce.tab.list[[i]])
        amce.tab.list[[i]]$set[1:4] <-  amce.tab.list[[i]]$set[5:8]
      }
      else amce.tab.list[[i]] <- amce.tab.list[[i]]
    }     
    amce.tab <- do.call("rbind",amce.tab.list)
    amce.tab$set <- factor(amce.tab$set)
    return(amce.tab)
  } 
  if(multi == F)   {
    get.amcetab(data, variables)
  }
  
}


### Figure 3: AMCEs for all attributes

res <- amce.tab(data = long.dat, 
                variables = c("mp.partypos", "mp.localroots", "mp.const", "mp.influence", "mp.policy", "mp.gender"),
                multi = F)
res$category <- factor(as.character(res$category), levels = rev(as.character(res$category)), order =T)
#write.csv(res, "amce-all.csv")# write results to csv file

# Full plot for all attributes
res <- res[2:nrow(res),] # chop off top empty layer
res <- subset(res, level != "baseline")# remove artificial 'baseline' rows
labels <- labels.full
ggplot(res, aes(x = category, y = AMCE, color = attribute)) + 
  geom_hline(yintercept = 0, linetype = "dashed", size = 0.5) +
  geom_pointrange(aes(ymin = ci.lo, ymax = ci.hi), size = 0.75) + 
  labs(y = effect.label, x = "") + 
  coord_flip() + 
  theme_bw() + 
  theme(axis.text = element_text(colour = "black")) +
  theme(legend.position = "none") +
  theme(text = element_text(size = 15)) +
  theme(axis.ticks.y = element_blank(), axis.text.y = element_text(hjust = 1), # remove ticks and justify
        axis.title.x = element_text(size = 13, vjust = 0)) + 
  scale_x_discrete(labels=labels)

```

Caption from @paper: "Figure 3. Estimated average marginal component effects of each MP attribute level compared to the baseline level of the attribute, estimated via ordinary least squares regression, with standard errors clustered by respondent. Bars show 95% confidence intervals"