---
title: "Milestone Six and a Half"
author: "Sam Lowry"
date: "4/14/2020"
output: bookdown::pdf_document2
bibliography: bib.bib
biblio-style: "apalike"
abstract: This is an extension of Campbell et al. (2019) which details two separate experiments which suggest that individuals think of politicians with local connections and that exibit behavioral localism more highly. I was able to replicate the entire article with the exceptions of table 1 and figure 2 because they visuals relating to methodology and not the results themselves. I will be conducting an extension which includes the use of stan_glm instead of lm as well as look at certain subgroups based upon location and party identification. I hope to find cool things:)
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(bookdown)
library(sandwich)
library(lmtest)
library(stargazer)
library(cowplot)
library(cobalt)
library(xtable)
library(devtools)
library(margins)
library(car)
library(foreign)
library(rms)
library(reshape2)
library(plyr)
library(arm)
```

# Introduction

@paper aims to answer the driving question of, "Why do politicians with strong local roots receive more electoral support?" by running and analyzing two separate studies. The first study uses a "paired profiles factorial vignette design" by asking subjects to rate hypothetical members of Parliament. The hypothetical members have varying levels of local roots as well as varying levels of "behavioral localism"—their track record of constituency service and if they act more so as a trustee or delegate. In the second study, subjects again considered hypothetical members of Parliament with varying levels of local roots. How, the subjects also received information on their political preferences and partisan loyalties. The first study depicted that the additional information swayed rankings, but local roots still seemed to have an association. The second study agreed with these results stating that, "even if voters are provided with a rich array of information about politicians’ behavior and ideological positioning, the effect of local roots remained positive and notable." The remainder of the article discusses the nuances of these results within the frame of the driving question.

Using R, I replicated @paper. The original code can be found in the \textit{The Journal of Politics} Dataverse.^[https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/C15VOD] All of my code for this paper including the extension is available in my Github repository.^[https://github.com/SamuelLowry/why_friends_and_neighbors_replication_paper.git]

# Literature Review

After the introduction, you will have a literature review, not dissimilar from the one in the paper you are replicating. (You do not get to assume that we have read the paper you are replicating. We haven’t. So, if something is worth understanding about the literature, then you need to tell us, and in your own words.) You also need to closely review any relevant literature that has come out since the paper was published. (We will take off points if a simple Google scholar search brings up a relevant article which you should have mentioned.) Of course, if a lot of time has passed and/or this is a particularly active area of research, there may be dozens of relevant articles. You can’t review them all. Pick the most important ones, especially those written by the same authors and/or using the same data and/or performing an analysis similar to your own extension.

# Possible Extensions

I have already been able to replicate all of the results from \textit{Why Friends and Neighbors? Explaining the Electoral Appeal of Local Roots} @paper by Rosie Campbell, Philip Cowley, Nick Vivyan, and Markus Wagner in the \textit{The Journal of Politics}. The next step is to improve upon their methods and make suggests as to what to do next. My thoughts are below:

1. The first step is to suggest using stan_glm from the rstanarm package instead of the simple lm. This allows for the use of generalized linear modeling instead of linear modeling with optional prior distributions for the coefficients—a Bayesian function.
  
2. Both studies examine how the attributes of the Members of Parliament influence views on behavioral localism and local roots. Nevertheless, the data does not look within many demographic categories which are collected about the subjects. How do these views change based upon individual political views, gender, education level etc. I aim therefore to also use priors to maybe weight for these separate groups to create a better picture of the UK electorate. 
  
3. Study 2 uses F-tests to see if there is interactions between Members of Parliaments' local ties and each remaining attribute. Page 140 in the textbook cautions against the use of such tests, for noisy data can give rise to insignificance with hypothesis testing even if there is some. Therefore it would be better to scrap this point or revise it. I am still in the process of determining a better alternative. 
  
4. In order to maybe make this study more reliable to extrapolate upon, we could delete all vignettes within the analysis where the Member of Parliament lives outside of the district which simply cannot occur with other legislators such as Congressmen in the United States which are required to live within their district. 

These extensions will hopefully better the article as a whole and clarify its implications. 

All analysis for this paper is available in my Github repository for this milestone is in the footnote below. ^[https://github.com/SamuelLowry/why_friends_and_neighbors_replication_paper.git]

\newpage

# References

<div id="refs"></div>

\newpage

# (APPENDIX) Appendix {-} 

# Appendix of Replicated Graphics

I was able to replicate table 2, figure 1, and figure 3. I was unable to replicate table 1 and figure 2 because they were not data related. They were merely visualizations displaying content about methods and experimental design. Table 1 depicts written descriptions of the hypothetical Members of Parliament present to subject. Figure 2 depicts a screenshot of the survey. 

### Table 2 {-} 

```{r data}
#loaded in the data from the first study

d <- readRDS("paper_files/study1data.rds")

```

```{r table2, warning=FALSE, results='asis'}
#warning = FALSE in order to get rid of unknown variable due to their code being wacl

#Here I pulled over their code but then tried to improve upon it, for currently the figure is unreadable. 

#models for this graphic and the table later on

m1 <- lm(nickminusphil ~ localtreat*behtreatsimple, data = d)
se1 <- sqrt(diag(vcovHC(m1)))

m2 <- lm(nickminusphil ~ localtreat*behtreatsimple +
           gender + agegrp + socgrade + qual
         , data = d)
se2 <- sqrt(diag(vcovHC(m2)))

m3 <- lm(nickminusphil ~ localtreat*behtreat, data = d)
se3 <- sqrt(diag(vcovHC(m3)))

m4 <- lm(nickminusphil ~ localtreat*behtreat +
           gender + agegrp + socgrade + qual
         , data = d)
se4 <- sqrt(diag(vcovHC(m4)))

#I took the code for table 2 from their code and made it output to Latex

stargazer(mget(paste0("m",1:4)),
          se = mget(paste0("se",1:4)),
          type = "latex",
          float = FALSE,
          dep.var.caption = "",
          dep.var.labels.include = FALSE,
          title = "", 
          #intercept.bottom = FALSE, intercept.top = TRUE,
          keep.stat = c("n", "rsq", "adj.rsq"),
          omit = "socgrade|agegrp|gender|qual",
          order = c("Constant", "^localtreatLocal roots$", 
                    "^behtreatsimpleBehavioural info$", 
                    "^behtreatConst. focus$", 
                    "^behtreatWestmin. focus$",
                    "^localtreatLocal roots:behtreatsimpleBehavioural info$",
                    "^localtreatLocal roots:behtreatConst. focus$",
                    "^localtreatLocal roots:behtreatWestmin. focus$"
          ),
          add.lines = list(c("Controls for voter characteristics?", 
                             rep(c("No","Yes"), 2))),
          covariate.labels = c("Intercept", "Local roots", "Behavioral localism information",
                               "Behavioral localism: High (vs. no info)",
                               "Behavioral localism: Low (vs. no info)",
                               "Local roots X Behavioral info.", 
                               "Local roots X High behavioral localism",
                               "Local roots X Low behavioral localism")
)
```

### Figure 1 {-} 

```{r figure1, warning = FALSE, cache = TRUE}

#warning is false to delete warning for unknown variable specified in code which does not change vizualization from the paper. 

#function needed for figure 1

predict.rob <- function(object, vcov,newdata){
  tt <- terms(object)
  if(missing(newdata)){ newdata <- x$model }
  else {
    Terms <- delete.response(tt)
    m <- model.frame(Terms, newdata, na.action = na.pass, 
                     xlev = object$xlevels)
    if (!is.null(cl <- attr(Terms, "dataClasses"))) 
      .checkMFClasses(cl, m)
    X <- model.matrix(Terms, m, contrasts.arg = object$contrasts)
    offset <- rep(0, nrow(X))
    if (!is.null(off.num <- attr(tt, "offset"))) 
      for (i in off.num) offset <- offset + eval(attr(tt, 
                                                      "variables")[[i + 1]], newdata)
    if (!is.null(object$call$offset)) 
      offset <- offset + eval(object$call$offset, newdata)
    mmDone <- FALSE
  }
  #m.mat <- model.matrix(x$terms,data=newdata)
  m.coef <- object$coef
  fit <- as.vector(X %*% object$coef)
  se.fit <- sqrt(diag(X%*%vcov%*%t(X)))
  return(list(fit=fit,se.fit=se.fit))
}


### Figure 1
#I was very confused about B here especially because of the variability and the "no information" section being higher. 
## Avg treatment effect of local roots with const and westmihn. info
out <- summary(margins(m4, vcov = vcovHC(m4), 
                       at = list(behtreat = c("No behavioural info", "Const. focus", "Westmin. focus"))))
out <- subset(out, factor == "localtreatLocal roots")
margins.m4 <- out 

## make margins plot
margins.comb <- margins.m4
margins.comb$behtreat.neat <- car:::recode(margins.comb$behtreat, 
                                           '"No behavioural info" = "Behavioral information treatment --\\nNo information (Vignettes 1-2)";
                                           "Westmin. focus" = "Behavioral information treatment --\\nLow behavioral localism (Vignettes 5-6)";
                                           "Const. focus" = "Behavioral information treatment --\\nHigh behavioral localism (Vignettes 3-4)"')
margins.comb$behtreat.neat <- factor(sub(" --", ":", margins.comb$behtreat.neat),
                                     levels = c("Behavioral information treatment:\nNo information (Vignettes 1-2)", 
                                                "Behavioral information treatment:\nLow behavioral localism (Vignettes 5-6)",
                                                "Behavioral information treatment:\nHigh behavioral localism (Vignettes 3-4)"
                                     ))
p1 <- ggplot(margins.comb, aes(x = factor, y = AME)) + 
  geom_hline(yintercept = 0, linetype = "dashed", size = 0.5) +
  geom_linerange(aes(x=factor, xend=factor, ymin=lower, ymax=upper), size = 0.6) +
  geom_point(size = 3.5, shape = 21, fill = "white") +
  labs(x = "", y = "") + 
  coord_flip() +
  facet_wrap( ~ behtreat.neat, ncol = 1) + 
  theme_bw() +
  theme(legend.position = "bottom") +
  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()) + 
  ggtitle("(b) Effect of MP local roots treatment") 




## predlevels for m4
#what is m4???
newdf <- data.frame(expand.grid(localtreat = factor(c("No local roots", "Local roots"), 
                                                    levels = levels(d$localtreat)),
                                behtreat = factor(levels(d$behtreat), levels = levels(d$behtreat))
),
gender = factor(levels(d$gender)[which.max(table(d$gender))], 
                levels = levels(d$gender)),
agegrp = factor(levels(d$agegrp)[which.max(table(d$agegrp))], 
                levels = levels(d$agegrp)),
socgrade = factor(levels(d$socgrade)[which.max(table(d$socgrade))], 
                  levels = levels(d$socgrade)),
qual = factor(levels(d$qual)[which.max(table(d$qual))], 
              levels = levels(d$qual))
)
preds <- predict.rob(m4, vcov = vcovHC(m4), newdata = newdf)
newdf$yhat <- preds$fit
newdf$se.yhat <- preds$se.fit
newdf$lo <- newdf$yhat - (1.96*newdf$se.yhat)
newdf$hi <- newdf$yhat + (1.96*newdf$se.yhat)
predlevels.m4 <- newdf


## make predlevels plot
#okay this is still the first plot. B still confuses me though. 
predlevels.comb <- predlevels.m4
predlevels.comb$behtreat.neat <- car:::recode(predlevels.comb$behtreat, 
                                              '"No behavioural info" = "Behavioral information treatment --\\nNo information (Vignettes 1-2)";
                                              "Westmin. focus" = "Behavioral information treatment --\\nLow behavioral localism (Vignettes 5-6)";
                                              "Const. focus" = "Behavioral information treatment --\\nHigh behavioral localism (Vignettes 3-4)"')
predlevels.comb$behtreat.neat <- factor(sub(" --", ":", predlevels.comb$behtreat.neat),
                                        levels = c("Behavioral information treatment:\nNo information (Vignettes 1-2)", 
                                                   "Behavioral information treatment:\nLow behavioral localism (Vignettes 5-6)",
                                                   "Behavioral information treatment:\nHigh behavioral localism (Vignettes 3-4)"
                                        ))

p2 <- ggplot(predlevels.comb, aes(x = localtreat, y = yhat)) + 
  geom_hline(yintercept = 0, linetype = "dashed", size = 0.5) +
  geom_linerange(aes(x=localtreat, xend=localtreat, ymin=lo, ymax=hi), size = 0.6) +
  geom_point(size = 3.5, shape = 21, fill = "white") +
  labs(x = "", y = "") + 
  coord_flip() +
  facet_wrap( ~ behtreat.neat, ncol = 1) + 
  theme_bw() +
  theme(legend.position = "bottom") + 
  ggtitle("(a) Predicted relative rating")



## Now combine aspects of above plots into 3 x 2 plot
pcomb <- plot_grid(p2, p1, align = "h", rel_widths = c(1,0.8))

pcomb
```

### Figure 3 {-} 

```{r figure3, warning = FALSE}

#warning is false to delete warning for 11 deletions caused by ggplot which does not change vizualization from the paper. 

#needed data

long.dat <- readRDS(file = "paper_files/study2data_long.rds")

### Create labels for plotting

# for full results
labels.full <- rev(expression(
  "", italic("Party & position (baseline = Labour left-wing)"), "Labour centre", "Conservative centre", "Conservative right-wing",
  "", italic("Local roots (baseline = lives elsewhere)"),"5 years in area", "20 years in area", "Grew up and lives in area", 
  "", italic("Constituency work (baseline = 1 day)"), "2 days", "3 days", "4 days",
  "", italic("Main policy influence (baseline = party)"), "constituents' views","own personal views",
  "", italic("Policy interests (baseline = economy and tax)"), "education and health",
  "", italic("MP sex (baseline = female)"), "male"))

# for x axis
effect.label <- "Change in probability of MP being preferred,\n relative to baseline"

#needed functions

add.top <- function(df, new.level){
  to.add <- data.frame(mean = c(NA,NA, 0), ci.lo = c(NA,NA, 0), ci.hi = c(NA,NA, 0),
                       category = rep("", 3), attribute = rep(df$attribute[1],3),
                       level = c("", " ", new.level))
  return(rbind(to.add, df))
}
add.justify <- function(df){
  df$left.justify <- rep(0, nrow(df))
  df$left.justify[2] <- 1
  return(df)
}

## Function to get regression-based AMCE estimates for each attribute level using 
## OLS estimator with clustered SEs (Hainmueller, Hopkins and Yammamoto 2014)

#Note to read up on the other literature above

get.amcetab <- function(data, variables, J = 2){    
  Nvar <- length(variables)
  amce.list <- vector("list", length = Nvar)
  
  for(i in 1:Nvar){ # get AMCE for each variable attribute
    fmla <- as.formula(paste("mp.preferred ~ ",variables[i], sep = ""))
    model <- ols(fmla, data = data, x = T, y = T) 
    # NOTE: The data for the model has to have no NAs on any model variables 
    # for the robcov(cluster()) function to work 
    model.clus <- robcov(model, cluster = data$ID, method = "efron")
    coef <- model.clus$coef[names(model.clus$coef)!="Intercept"]
    se.clus <- sqrt(diag(model.clus$var))
    se.clus <- se.clus[names(se.clus)!="Intercept"]       
    sub.tab <- data.frame("AMCE" = coef, 
                          "ci.lo" = coef - (1.96*se.clus),
                          "ci.hi" = coef + (1.96*se.clus),
                          "cluster.se" = se.clus)
    sub.tab$category <- names(coef)
    sub.tab <- cbind(sub.tab, colsplit(sub.tab$category, "=", c("attribute","level")))
    sub.tab$level <- as.character(sub.tab$level)    
    row.names(sub.tab) <- NULL
    # add in gaps and baselines
    to.add <- data.frame(AMCE = c(NA,NA, 0), ci.lo = c(NA,NA, 0), ci.hi = c(NA,NA, 0),
                         cluster.se = c(NA,NA, 0),
                         category = rep("", 3), attribute = rep(sub.tab$attribute[1],3),
                         level = c("", " ", "baseline"))
    amce.list [[i]] <- rbind(to.add, sub.tab)
  } 
  amce.tab <- do.call("rbind", amce.list)
  # re-make initial labels column
  amce.tab$category <- paste(amce.tab$attribute, amce.tab$level, sep = ": ")
  # make this into ordered factor
  amce.tab$category <- factor(amce.tab$category, levels = rev(amce.tab$category), order =T)    
  
  return(amce.tab)
}

## Function that calls get.amcetab for multiple predictors and combines results

amce.tab <- function(data, variables, multi = F, same.party = F){
  # data must be a single data frame or a list of data frames (if multi = T)
  # with named elements
  # Also relies on specific ordering of explanatory variables
  if(multi == T & same.party == F){
    amce.tab.list <- list(NA, length = length(data))
    for(i in 1:length(data)){
      tmp <- get.amcetab(data[[i]], variables = variables)
      tmp$set <- rep(names(data)[i], nrow(tmp))
      amce.tab.list[[i]] <- tmp
    }
    amce.tab <- do.call("rbind",amce.tab.list)
    amce.tab$set <- factor(amce.tab$set)
    return(amce.tab)
  }
  if(multi == T & same.party == T){
    amce.tab.list <- list(NA, length = length(data))
    for(i in 1:length(data)){
      vars <- if(grepl("same party", names(data)[i])==T|grepl("Same Party", names(data)[i])==T) variables[2:length(variables)] else variables
      tmp <- get.amcetab(data[[i]], variables = vars)
      tmp$set <- rep(names(data)[i], nrow(tmp))
      amce.tab.list[[i]] <- tmp
    }
    names(amce.tab.list) <- names(data)
    diff.party <- amce.tab.list[grepl("same party", names(amce.tab.list))==F&
                                  grepl("Same Party", names(amce.tab.list))==F]
    same.party <- amce.tab.list[grepl("same party", names(amce.tab.list))==T |
                                  grepl("Same Party", names(amce.tab.list))==T]
    to.add <- data.frame(AMCE = rep(NA, 4), ci.lo = rep(NA, 4), ci.hi =  rep(NA, 4),
                         cluster.se =  rep(NA, 4),
                         category =  diff.party[[1]]$category[1:4], 
                         attribute =  diff.party[[1]]$attribute[1:4], 
                         level = diff.party[[1]]$level[1:4],
                         set = rep(NA, 4))
    for(i in 1:length(data)){                     
      if(grepl("same party", names(data)[i])==T|grepl("Same Party", names(data)[i])==T){
        amce.tab.list[[i]] <- rbind(to.add,amce.tab.list[[i]])
        amce.tab.list[[i]]$set[1:4] <-  amce.tab.list[[i]]$set[5:8]
      }
      else amce.tab.list[[i]] <- amce.tab.list[[i]]
    }     
    amce.tab <- do.call("rbind",amce.tab.list)
    amce.tab$set <- factor(amce.tab$set)
    return(amce.tab)
  } 
  if(multi == F)   {
    get.amcetab(data, variables)
  }
  
}


### Figure 3: AMCEs for all attributes

res <- amce.tab(data = long.dat, 
                variables = c("mp.partypos", "mp.localroots", "mp.const", "mp.influence", "mp.policy", "mp.gender"),
                multi = F)
res$category <- factor(as.character(res$category), levels = rev(as.character(res$category)), order =T)
#write.csv(res, "amce-all.csv")# write results to csv file

# Full plot for all attributes
res <- res[2:nrow(res),] # chop off top empty layer
res <- subset(res, level != "baseline")# remove artificial 'baseline' rows
labels <- labels.full
ggplot(res, aes(x = category, y = AMCE, color = attribute)) + 
  geom_hline(yintercept = 0, linetype = "dashed", size = 0.5) +
  geom_pointrange(aes(ymin = ci.lo, ymax = ci.hi), size = 0.75) + 
  labs(y = effect.label, x = "") + 
  coord_flip() + 
  theme_bw() + 
  theme(axis.text = element_text(colour = "black")) +
  theme(legend.position = "none") +
  theme(text = element_text(size = 15)) +
  theme(axis.ticks.y = element_blank(), axis.text.y = element_text(hjust = 1), # remove ticks and justify
        axis.title.x = element_text(size = 13, vjust = 0)) + 
  scale_x_discrete(labels=labels)

```

